---
title: "Assignment 1"
author: "Songnan QUAN"
date: "2018/9/24"
output: html_document
---


## Exercise 1: Working with RMarkdown files
R is a free software environment for statistical computing and graphics.


## Exercice 2: Starting R programming
```{r}
possible_outcomes <- c(0, 1, 2, 3, 4, 5)
outcome_probabilities <- c(0.1, 0.5, 0.2, 0.1, 0.05, 0.05)
n_data_points <- 400
set.seed(1)
fake_data_points <- sample(possible_outcomes,
                           n_data_points,
                           replace=T,
                           prob=outcome_probabilities)
set.seed(NULL)
fake_data_set <- tibble::data_frame(`Fake measurement`=fake_data_points)
```

```{r}
ggplot2::ggplot(fake_data_set, ggplot2::aes(x=`Fake measurement`)) + ggplot2::geom_histogram(bins=5, colour="black", fill="lightgrey")
```

Statement 1. pass
  
Statement 2. this assgnment is exactely like the first line, which is most probably 

Statement 3.

Statement 4.

Statement 5

Statement 6


## Exercice 3: More R programming

### Sub-exercise 3-a

Load contents of the file "functions.R"
```{r}
source("functions.R")
```

Test the function "sum_column(d, var)"
```{r}
print(sum_column(iris, "Sepal.Length"))
print(sum_column(iris, "Species"))
print(sum_column(warpbreaks, "breaks"))
```

### Sub-exercise 3-b
Test the function "my_sum(x)"
```{r}
print(my_sum(iris$Sepal.Length))
print(my_sum(iris$Species))
print(my_sum(warpbreaks$breaks))
```

### Sub-exercise 3-c
Test the function "sum_diveded_by(x, k)"
```{r}
print(sum_divided_by(iris$Sepal.Length, 12))
print(sum_divided_by(iris$Species, 22))
print(sum_divided_by(iris$Sepal.Length, "Not numeric"))
print(sum_divided_by(warpbreaks$breaks, -12))
```

### Sub-exercise 3-d
Test the function "my_mean(x)"
```{r}
print(my_mean(iris$Sepal.Length))
print(my_mean(iris$Species))
print(my_mean(warpbreaks$breaks))
```


## Exercice 4

### Sub-exercise 4-a
```{r}
print(grouped_violin_plot(iris, "Sepal.Length", "Species"))
```

### Sub-exercise 4-b
```{r}
p <- grouped_violin_plot(iris, "Sepal.Length", "Species")
# YOUR CODE HERE: Change the colour scheme for the interior of the three violin plots
#                 to anything else at all.
p <- p + ggplot2::scale_fill_manual(values=c("yellow","blue","brown"))
# YOUR CODE HERE: Add a main title that says "Iris data".
p <- p + ggplot2::labs(title="Iris data")

print(p)
```




## Exercice 5